Testing and Isolation Efficacy:\\Insights from a Simple Epidemic Model

### 2022-03-06 manuscript_BMB.tex
correcting Fred's name
Meeting with Ali
inserted our responses in manuscript, response file cleaned up

\newcommand{\fref}[1]{Fig.~\ref{#1}}
\newcommand{\appref}[1]{Appendix~\ref{app:#1}}
% \newcommand{\Rlogo}{R\xspace}
\newcommand{\percap}{\emph{per capita}\xspace}
\newcommand{\Rnum}{\ensuremath{\mathcal{R}_0}\xspace}
\newcommand{\covid}{COVID-19\xspace}
\newcommand{\pro}[1]{\ensuremath{\frac{\partial #1}{\partial \rho}}}
\newcommand{\pder}[2]{\ensuremath{\frac{\partial#1}{\partial#2}}} %\pder y{x}
\newcommand{\testing}[1]{\ensuremath{{\cal T}_{#1}}\xspace}
\newcommand{\testinghat}[1]{\ensuremath{\hat{\cal T}_{#1}}\xspace}
\newcommand{\testtarget}{\ensuremath{w\_{IS}}}
\newcommand{\oldtesttarget}{\ensuremath{\frac{w_I}{w_S}}\xspace}
\newcommand*\subtxt[1]{_{\textnormal{#1}}}
% \newcommand{\rev}[1]{\comment{red}{Revised}{#1}}
%% Roman subscript
\DeclareRobustCommand\_{\ifmmode\expandafter\subtxt\else\textunderscore\fi}

@@

\institute{Ali Gharouni \at
              Department of Mathematics and Statistics, McMaster University, Hamilton, Canada \\
              Tel.: +100-00-000000\\
              Fax: +100-00-000000\\
              \email{agharoun@uottawa.ca}\\
              \emph{Present address:}
              Department of Mathematics and Statistics, University of Ottawa, Ottawa, Ontario \\%  if needed\\
              \email{agharoun@uottawa.ca}\\
           \and
           F.M. Abdelmalek \at
              Department of Mathematics and Statistics, McMaster University, Hamilton, Canada \\
              \email{abdelf1@mcmaster.ca}\\  
           \and
           David J. D. Earn \at
              Department of Mathematics and Statistics, McMaster University, Hamilton, Canada\\
              Michael G. DeGroote Institute for Infectious Disease Research, McMaster University, Hamilton, Canada\\
              \email{earn@math.mcmaster.ca}\\
           \and
          Jonathan Dushoff \at
              Department of Biology, McMaster University, Hamilton, Canada\\
              Michael G. DeGroote Institute for Infectious Disease Research, McMaster University, Hamilton, Canada\\
              South African Centre for Epidemiological Modelling and Analysis, University of Stellenbosch, Stellenbosch,               South Africa\\
              \email{dushoff@mcmaster.ca} \\
           \and
          Benjamin M. Bolker \at
              Department of Mathematics and Statistics, McMaster University, Hamilton, Canada \\
              Department of Biology, McMaster University, Hamilton, Canada\\
              Michael G. DeGroote Institute for Infectious Disease Research, McMaster University, Hamilton, Canada\\
              \email{bolker@mcmaster.ca}
}

@@

In this paper, we have developed and analyzed a simple compartmental model that combines epidemiological dynamics---as defined by a simple SIR model---with the dynamics of testing and isolation. Our model is a caricature: it models the most basic feedbacks between epidemic and testing processes, but does not attempt to incorporate the many known complications of COVID-19 epidemiology (e.g., exposed, pre-symptomatic, and asymptomatic compartments \citep{kain2021chopping}; time-varying testing rates; behavioural dynamics \citep{weitz2020awareness}); Thus, it is most appropriate for assessing the \emph{qualitative} phenomena that arise from the interactions between transmission dynamics and testing, rather than for making quantitative predictions or guiding pandemic responses.

@@

Although testing and tracing is a key part of infection control strategies, mathematical epidemiologists have typically analyzed it with detailed models designed to inform particular public health efforts \citep{endo2020implication,hellewell2020feasibility,jenness2020modeling}, rather than analyzing simple but general models of the feedback between testing and transmission dynamics.
There have been several modeling studies of testing and tracing dynamics and their interaction with epidemiological dynamics. In the context of repeated screening and random testing of isolated populations (such as the members of a university), \cite{bergstrom2020frequency} provided analytical results quantifying the effects that proactive screening of asymptomatic individuals and isolation of confirmed-positive cases could have in reducing the spread of disease. 
\cite{rogers2021high} simulated a SEIR model with testing and isolation; they similarly suggest a strategy of rapid testing with antigen tests and the subsequent isolation of confirmed-positive individuals.
% reviewer1.com1
\cite{friston2021testing} model the effects of self-isolation on testing and tracing with a focus on projections under different testing and tracing scenarios. They conclude that the emergence of a second wave depends almost primarily on the rate at which immunity is lost and that it is necessary to track asymptomatic individuals in order to control the outbreak. 
Our modeling approach differs from these previous efforts in that it examines the effects of test-return rates and of different levels of testing focus, from random to highly targeted. We hope this paper will inspire further explorations of the fundamental properties of epidemic models that incorporate explicit testing processes.

>>>>

\newcommand{\fady}[1]{\comment{cyan}{Fady}{#1}}
\newcommand{\ali}[1]{\comment{magenta}{Ali}{#1}}
\newcommand{\jd}[1]{\comment{blue}{JD}{#1}}
\newcommand{\david}[1]{\comment{orange}{DJDE}{#1}}
\newcommand{\bmb}[1]{\comment{red}{BMB}{#1}}
\newcommand{\todo}[1]{\comment{red}{TODO}{#1}}
\newcommand{\new}[1]{\comment{red}{NEW}{#1}}
\newcommand{\needref}{\textcolor{red}{(REFS?)}}

\newcommand{\fref}[1]{Fig.~\ref{#1}}
\newcommand{\appref}[1]{Appendix~\ref{app:#1}}
% \newcommand{\Rlogo}{R\xspace}
\newcommand{\percap}{\emph{per capita}\xspace}
\newcommand{\Rnum}{\ensuremath{\mathcal{R}_0}\xspace}
\newcommand{\covid}{COVID-19\xspace}
\newcommand{\pro}[1]{\ensuremath{\frac{\partial #1}{\partial \rho}}}
\newcommand{\pder}[2]{\ensuremath{\frac{\partial#1}{\partial#2}}} %\pder y{x}
\newcommand{\testing}[1]{\ensuremath{{\cal T}_{#1}}\xspace}
\newcommand{\testinghat}[1]{\ensuremath{\hat{\cal T}_{#1}}\xspace}
\newcommand{\testtarget}{\ensuremath{w\_{IS}}}
\newcommand{\oldtesttarget}{\ensuremath{\frac{w_I}{w_S}}\xspace}
\newcommand*\subtxt[1]{_{\textnormal{#1}}}
\newcommand{\rev}[1]{\comment{red}{Revised}{#1}}
%% Roman subscript
\DeclareRobustCommand\_{\ifmmode\expandafter\subtxt\else\textunderscore\fi}

@@

\institute{Ali Gharouni \at
              Department of Mathematics and Statistics, McMaster University, Hamilton, Canada \\
              Tel.: +100-00-000000\\
              Fax: +100-00-000000\\
              \email{agharoun@uottawa.ca}\\
              \emph{Present address:}
              Department of Mathematics and Statistics, University of Ottawa, Ottawa, Ontario \\%  if needed\\
              \email{agharoun@uottawa.ca}\\
           \and
           Fred .M. Abdelmalek \at
              Department of Mathematics and Statistics, McMaster University, Hamilton, Canada \\
              \email{abdelf1@mcmaster.ca}\\  
           \and
           David J. D. Earn \at
              Department of Mathematics and Statistics, McMaster University, Hamilton, Canada\\
              Michael G. DeGroote Institute for Infectious Disease Research, McMaster University, Hamilton, Canada\\
              \email{earn@math.mcmaster.ca}\\
           \and
          Jonathan Dushoff \at
              Department of Biology, McMaster University, Hamilton, Canada\\
              Michael G. DeGroote Institute for Infectious Disease Research, McMaster University, Hamilton, Canada\\
              South African Centre for Epidemiological Modelling and Analysis, University of Stellenbosch, Stellenbosch,               South Africa\\
              \email{dushoff@mcmaster.ca} \\
           \and
          Benjamin M. Bolker \at
              Department of Mathematics and Statistics, McMaster University, Hamilton, Canada \\
              Department of Biology, McMaster University, Hamilton, Canada\\
              Michael G. DeGroote Institute for Infectious Disease Research, McMaster University, Hamilton, Canada\\
              \email{bolker@mcmaster.ca}
}

@@

In this paper, we have developed and analyzed a simple compartmental model that combines epidemiological dynamics---as defined by a simple SIR model---with the dynamics of testing and isolation. Our model is a caricature: it models the most basic feedbacks between epidemic and testing processes, but does not attempt to incorporate the many known complications of COVID-19 epidemiology (e.g., exposed, pre-symptomatic, and asymptomatic compartments \citep{kain2021chopping}; time-varying testing rates; behavioural dynamics \citep{weitz2020awareness}); 
% reviewer2:com1
\rev{Further, our model ignores the fact that the testing and isolation parameters can change over time due to public health responses. In other words, our model makes an assumption of ``independence'': we assume that testing and isolation affect the epidemic progression, but we do not account for the fact that "in real life", the epidemic progression is also likely to affect the testing and isolation strategies.}
Thus, it is most appropriate for assessing the \emph{qualitative} phenomena that arise from the interactions between transmission dynamics and testing, rather than for making quantitative predictions or guiding pandemic responses.

@@

% TODO reviewer1:com2
\rev{Regarding the incorporation of an exposed class or asymptomatic and infectious compartment to the current model; Incorporating the extra compartments (exposed, asymptomatic and infectious) would effect the testing weights and isolation efficacy parameters. In particular, we know that people know something about their exposure (assuming we don't know about symptoms). We know that there is a bias towards testing infected people, due to having some knowledge of risk. Testing people of known exposures will increase testing weight $w_I$, this is testing and tracing. Also, exposed people presumably practice more isolation, thus $\theta\_w$ will increase and consequently $\Rnum$ will decrease.} \fady{In a less trivial sense, the existence of an exposed class could make any difference in our model only if the testing and isolation parameters are different for the exposed class than the infected class. That is, I think that if we added an exposed class in our model but set the testing intensity and isolation strength to be the same as the infected class, then nothing would change in our model.}

Although testing and tracing is a key part of infection control strategies, mathematical epidemiologists have typically analyzed it with detailed models designed to inform particular public health efforts \citep{endo2020implication,hellewell2020feasibility,jenness2020modeling}, rather than analyzing simple but general models of the feedback between testing and transmission dynamics.
There have been several modeling studies of testing and tracing dynamics and their interaction with epidemiological dynamics. In the context of repeated screening and random testing of isolated populations (such as the members of a university), \cite{bergstrom2020frequency} provided analytical results quantifying the effects that proactive screening of asymptomatic individuals and isolation of confirmed-positive cases could have in reducing the spread of disease. 
\cite{rogers2021high} simulated a SEIR model with testing and isolation; they similarly suggest a strategy of rapid testing with antigen tests and the subsequent isolation of confirmed-positive individuals.
% TODO reviewer1:com1
\rev {\cite{muller2021mathematical} simulated a structured SEIR-type model. Their model incorporated different testing scenarios -- including gateway testing (what ``gateway testing'' is? ref?), surveillance testing, and contact tracing -- as well as individual level control measures such as mask wearing and social distancing. They indicate the benefit of gateway testing in conjunction with effective contact tracing or robust surveillance testing in controling the spread of the infection. Under such approaches, individuals must practice increased levels of social distancing or self- isolation until they have achieved a series of confirmed negative tests. It is notable that while this type of time- dependent testing and self-isolation protocol might not fit well within the framework of linear stability of a disease-free equilibrium, the relationship between increased $\theta_w$ and the benefits of a longer waiting period $1/\omega$ seems to indicate the possibility that combining waiting for results and self-isolation can help to stem early outbreaks (e.g. at the beginning of a university term).}
\cite{friston2021testing} model the effects of self-isolation on testing and tracing with a focus on projections under different testing and tracing scenarios. They conclude that the emergence of a second wave depends almost primarily on the rate at which immunity is lost and that it is necessary to track asymptomatic individuals in order to control the outbreak. 
Our modeling approach differs from these previous efforts in that it examines the effects of test-return rates and of different levels of testing focus, from random to highly targeted. We hope this paper will inspire further explorations of the fundamental properties of epidemic models that incorporate explicit testing processes.

% TODO reviewer2:com2 
\rev{ The potential future work of this project include:
(i) Incorporating the asymptomatic and symptomatic compartments to the model and verify the present results. 
(ii) Quantify the testing weights, when we incorporate asymptomatic and symptomatic compartments to the model. In particular, We know that not all symptomatic people are the same. people know something about their exposure, and not necessarily about symptoms. We know that there is a bias towards testing infected people, due to having some knowledge of risk. It is harder to quantify that than quantifying symptom/no symptom but we can say that would shift if we have a policy of screening people of high risk areas will push things towards infected people. Also testing people of known exposures will increase testing weight for infected people $w_I$, this is exactly testing and tracing. It is much harder to quantify that. In principle if we knew enough of the case report, hospitalizations, test positivity, death, we could make an estimate of $w_X$'s. Also note that $w_X$'s don't stay the same because it is all bound up with capacity because we tend to bias towards testing people who are more likely be infected and the more testing capacity we have the more we are willing to test more people less likely to be infected. Thus there is a relationship between testing capacity and the $w_X$'s because our testing policy changes as the testing capacity changes. Except for the symptomatic example, it is very hard to quantify the effect of a particular testing policy on the $w_X$'s. In short, "test positivity tells a lot about testing weights"; It is hard to know exactly how much information there is and how much we can estimate that.}
\fady{
our model makes the counterintuitive suggestion that increased testing rate could increase $\Rnum$. However, note that in our model, we made the assumption that once an individual is in the ``waiting'' compartment, they cannot be tested again until the test result returns. Thus, when the test return time is very long, this creates a massive time-delay where an individual may become infected while waiting for the test result, and then the test result comes back as negative, and so they believe they are negative when they are actually positive (and so they do not self-isolate at all, under the belief that they are negative).
So, in this case, it would be beneficial to actually re-test people even if their first test result has not come back. In fact, one could probably conceive of ``testing breadth'' (which roughly corresponds to the number of different people you test over some period of time) vs. ``testing depth (which corresponds to the number of times you test a single person over a period of time). Note that testing breadth gives us granular information ``in space but not in time'' (i.e., it tells us how many people are or are not infected at a single point in time), whereas testing depth gives us granular information ``in time but not in space''. The pathological situation in our model can be viewed as an imbalance between testing depth and breadth, where the testing strategy is overly-broad but not sufficiently deep.
In particular, one could build models that differentiate/partition ``testing intensity'' into ``testing breadth'' and ``testing depth''. In such a model, there should always exist some allocation of breadth and depth that makes it so that increasing the overall testing intensity is beneficial (i.e., if we choose the right strategy, more testing should always be good).
The most important point of all this: while the exact effect we identified in our model (that more testing can increase $\Rnum$ if done incorrectly) is unlikely to happen in real life, a weaker ``sister effect'' probably happens in real life all the time: we may be allocating our testing resources in the wrong breadth vs. depth ratio. Our model ``proves'' that pure-breadth is not always the optimal strategy (because, in fact, it can increase $\Rnum$). So, a more realistic future question is: what is the optimal allocation between breadth and depth that decreases $\Rnum$ most sharply for a given overall testing intensity? For example, in our model, when we increase testing intensity, we are mostly increasing breadth. So, even on parameter sets in our model where increasing rho decreases $\Rnum$, we may still be ``missing out'' by focusing only on breadth and not depth.
}
\david{These are thoughtful ideas from Fred.  Perhaps they could be compressed to a couple of sentences describing a future direction worth pursuing.}

### 2022-03-06 response1_BMB.tex
Meeting with Ali
inserted our responses in manuscript, response file cleaned up

\com 1 {\it The main surprising results about the possibility of R0 increasing with increased testing intensity or decreasing with increased delays seem particularly intertwined with the behavior displayed by individuals who are waiting for their test results. In particular, having long delays can make versions of the model with high $\theta\_w$ effectively treat these waiting individuals into a partially socially-distanced or quarantined compartment, while, in versions in which waiting individuals do not change their behavior, increased asymptomatic testing can provide extra time to miss new infectious. This connection between behavior of waiting and confirmed individuals and how testing impacts R0 makes me curious about a few aspects of combining testing with social distancing.

@@

\res 1 
We now have added several lines and the suggested reference [1] to the end of the discussion to acknowledge the ``gateway testing'' and the potential benefit of our modelling results in controling the disease spread.

\rev {\cite{muller2021mathematical} simulated a structured SEIR-type model. Their model incorporated different testing scenarios -- including gateway testing \fady{what ``gateway testing'' is? ref?}, surveillance testing, and contact tracing -- as well as individual level control measures such as mask wearing and social distancing. They indicate the benefit of gateway testing in conjunction with effective contact tracing or robust surveillance testing in controling the spread of the infection. Under such approaches, individuals must practice increased levels of social distancing or self- isolation until they have achieved a series of confirmed negative tests. It is notable that while this type of time- dependent testing and self-isolation protocol might not fit well within the framework of linear stability of a disease-free equilibrium, the relationship between increased $\theta_w$ and the benefits of a longer waiting period $1/\omega$ seems to indicate the possibility that combining waiting for results and self-isolation can help to stem early outbreaks (e.g. at the beginning of a university term).}

@@

\rev{ Regarding the incorporation of an exposed class or asymptomatic and infectious compartment to the current model; 
Incorporating the extra compartments (exposed, asymptomatic and infectious) would effect the testing weights and isolation efficacy parameters. In particular, we know that people know something about their exposure (assuming we don't know about symptoms). We know that there is a bias towards testing infected people, due to having some knowledge of risk. Testing people of known exposures will increase testing weight $w_I$, this is testing and tracing. Also, exposed people presumably practice more isolation, thus $\theta\_w$ will increase and consequently $\Rnum$ will decrease. }
\fady{In a less trivial sense, I think that the existence of an exposed class could make any difference in our model only if the testing and isolation parameters are different for the exposed class than the infected class. That is, I think that if we added an exposed class in our model but set the testing intensity and isolation strength to be the same as the infected class, then nothing would change in our model.}

@@

\res 3
We now have added a line in the manuscript to describe the parameters involved in the DFE before Equation (4).

\rev {The DFE depends on \percap testing intensity $\rho$, the rate of test return $\omega$, and the population size $N$.}

@@

\res 4
We have added a line in the manuscript in Section A.4 of the appendix to clarify the fact that Eq. 27 is a direct result of differentiating $\Delta$ in Eq.7 with respect to $w_{IS}$.

\rev{Using the expression for the effectiveness of control parameter $\Delta$ in eq.~\ref{eq:del4a}, gives}

@@

@@

\res 1
We now have added a line in the manuscript (the first paragraph of the Discussion section) to clarify what we mean by the term ``caricature''.

Our model is a caricature: it models the most basic feedbacks between epidemic and testing processes, but does not attempt to incorporate the many known complications of COVID-19 epidemiology (e.g., exposed, pre-symptomatic, and asymptomatic compartments \citep{kain2021chopping}; time-varying testing rates; behavioural dynamics \citep{weitz2020awareness}); \rev{the array consisting of multidirectional subtle interplay between epidemiology, behaviors and public health policies.} Thus, it is most appropriate for assessing the \emph{qualitative} phenomena that arise from the interactions between transmission dynamics and testing, rather than for making quantitative predictions or guiding pandemic responses.

\ali {note sure what we should discuss more than what we have in the manuscript!}
\fady{I think what the reviewer means is that our model ignores the fact that the testing and isolation parameters can change over time due to public health responses. In other words, our model makes an assumption of "independence": we assume that testing and isolation affect the epidemic progression, but we do not account for the fact that "in real life", the epidemic progression is also likely to affect the testing and isolation strategies. }

@@

\res 2
We have added some lines to the discussion section of the manuscript to include some potential future work.

\rev{ The potential future work of this project include:
\begin{enumerate}
\item
Incorporating the asymptomatic and symptomatic compartments to the model and verify the present results. 
\item
Quantify the testing weights, when we incorporate asymptomatic and symptomatic compartments to the model. In particular, We know that not all symptomatic people are the same. people know something about their exposure, and not necessarily about symptoms. We know that there is a bias towards testing infected people, due to having some knowledge of risk. It is harder to quantify that than quantifying symptom/no symptom but we can say that would shift if we have a policy of screening people of high risk areas will push things towards infected people. Also testing people of known exposures will increase testing weight for infected people $w_I$, this is exactly testing and tracing. It is much harder to quantify that. In principle if we knew enough of the case report, hospitalizations, test positivity, death, we could make an estimate of $w_X$'s. Also note that $w_X$'s don't stay the same because it is all bound up with capacity because we tend to bias towards testing people who are more likely be infected and the more testing capacity we have the more we are willing to test more people less likely to be infected. Thus there is a relationship between testing capacity and the $w_X$'s because our testing policy changes as the testing capacity changes. Except for the symptomatic example, it is very hard to quantify the effect of a particular testing policy on the $w_X$'s. In short, "test positivity tells a lot about testing weights"; It is hard to know exactly how much information there is and how much we can estimate that.
\item
test
\end{enumerate}
}

\fady{
our model makes the counterintuitive suggestion that increased testing rate could increase $\Rnum$. However, note that in our model, we made the assumption that once an individual is in the ``waiting'' compartment, they cannot be tested again until the test result returns. Thus, when the test return time is very long, this creates a massive time-delay where an individual may become infected while waiting for the test result, and then the test result comes back as negative, and so they believe they are negative when they are actually positive (and so they do not self-isolate at all, under the belief that they are negative).
So, in this case, it would be beneficial to actually re-test people even if their first test result has not come back. In fact, one could probably conceive of ``testing breadth'' (which roughly corresponds to the number of different people you test over some period of time) vs. ``testing depth (which corresponds to the number of times you test a single person over a period of time). Note that testing breadth gives us granular information ``in space but not in time'' (i.e., it tells us how many people are or are not infected at a single point in time), whereas testing depth gives us granular information ``in time but not in space''. The pathological situation in our model can be viewed as an imbalance between testing depth and breadth, where the testing strategy is overly-broad but not sufficiently deep.
In particular, one could build models that differentiate/partition ``testing intensity'' into ``testing breadth'' and ``testing depth''. In such a model, there should always exist some allocation of breadth and depth that makes it so that increasing the overall testing intensity is beneficial (i.e., if we choose the right strategy, more testing should always be good).
The most important point of all this: while the exact effect we identified in our model (that more testing can increase $\Rnum$ if done incorrectly) is unlikely to happen in real life, a weaker ``sister effect'' probably happens in real life all the time: we may be allocating our testing resources in the wrong breadth vs. depth ratio. Our model ``proves'' that pure-breadth is not always the optimal strategy (because, in fact, it can increase $\Rnum$). So, a more realistic future question is: what is the optimal allocation between breadth and depth that decreases $\Rnum$ most sharply for a given overall testing intensity? For example, in our model, when we increase testing intensity, we are mostly increasing breadth. So, even on parameter sets in our model where increasing rho decreases $\Rnum$, we may still be ``missing out'' by focusing only on breadth and not depth.
}

>>>>

% JD try to write text
\com 1 {\it The main surprising results about the possibility of R0 increasing with increased testing intensity or decreasing with increased delays seem particularly intertwined with the behavior displayed by individuals who are waiting for their test results. In particular, having long delays can make versions of the model with high $\theta\_w$ effectively treat these waiting individuals into a partially socially-distanced or quarantined compartment, while, in versions in which waiting individuals do not change their behavior, increased asymptomatic testing can provide extra time to miss new infectious. This connection between behavior of waiting and confirmed individuals and how testing impacts R0 makes me curious about a few aspects of combining testing with social distancing.

@@

\res 1 
We now have added several lines and the suggested reference [1] to the end of the discussion to acknowledge the ``gateway testing'' and the potential benefit of our modelling results in controling the disease spread.    
% {search for reviewer1:com1 in the manuscript_BMB.tex}

@@

% JD try to write text
% {search for reviewer1:com2 in the manuscript_BMB.tex}

@@

\res 3
We now have added a line in the manuscript to describe the parameters involved in the DFE before Equation (4).
% {search for reviewer1:com3 in the manuscript_BMB.tex}

@@

\res 4
We have added a line in the manuscript in Section A.4 of the appendix to clarify the fact that Eq. 27 is a direct result of differentiating $\Delta$ in Eq.7 with respect to $w_{IS}$.
% {search for reviewer1:com4 in the manuscript_BMB.tex}

@@

%% JD to look at all of Rev 2

@@

\res 1
We now have added a line in the manuscript (the first paragraph of the Discussion section) to clarify what we mean by the term ``caricature''. 
% {search for reviewer2:com2 in the manuscript_BMB.tex}

@@

\res 2
We have added some lines to the discussion section of the manuscript to include some potential future work.
% { search for reviewer2:com2 in the manuscript_BMB.tex}
